Comparative study of Dask and Spark for neuroimaging pipelines

### 2019-06-12 latex/acl2019.tex
exp1 -- gantt chart

%% Baseline gantt chart
\subsection{Experimentation 1: Baseline timeline}
From Figure \ref{fig:inc_gantt} the execution time
is similar in Dask and Spark. However Spark takes more time to save the data to disk.
This could be due to the FIFO scheduler that tends to have the first set of save
consequent thus saturating the nfs. Also serialization could have an effect. It looks
like the nfs could be a bottleneck when reading (writing) data from (to) the
application.

Dask scheduler seems to have strange behaviour in Figure \ref{fig:inc_gantt}. It
often wait before scheduling tasks that we would expect to be scheduled right away.
We currently don't have explication for this behaviour. This could be explained by
task rescheduled to other workers.

Also, the same length does not seem to be homogeneous. This might be due to caching
effect either with the main memory or the nfs.

>>>>

%% Baseline gantt chart
\subsection{Experimentation 1: Baseline timeline}
From Table \ref{tb:inc-base} and Figure \ref{fig:inc_gantt} the framework have
similar makespan however the time spend for each type of task differ significantly.
Spark tends to spend more time than other framework for IO however it has a much
lower overhead. dask delayed and futures have a the loowest IO time but a much higher
overhead. Dask bag stand in the middle for both IO and overhead. Compute time is
approximately the same for all frameworks.

\begin{table}[h]
  \resizebox{\columnwidth}{!}{
    \begin{tabular}{|l|l|l|l|l|l|}
    \hline
    Framework    & Read     & Compute & Write    & Overhead & Total    \\ \hline
    Spark        & 34465.22 & 5117.90 & 22679.15 & 17075.94 & 79338.22 \\ \hline
    Dask.bag     & 36863.32 & 5120.80 & 15448.91 & 21387.82 & 78820.86 \\ \hline
    Dask.delayed & 32769.47 & 5119.32 & 11372.86 & 26198.90 & 75460.56 \\ \hline
    Dask.futures & 31891.29 & 5120.47 & 11269.66 & 27983.72 & 76265.14 \\ \hline
    \end{tabular}
  }
  \caption{Distirbution of the execution time in seconds}
  \label{tb:inc-base}
 \end{table}
